Simulating null distributions

### 2020-08-20 null_distribution.Rmd
update null_distribution

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('check.R')
```

@@

@@

From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a normal distribution when the underlying observations are drawn from a N(5, 10) distribution. Let us check, if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2). Here, we fix the number of levels to 20.

@@

For facets, first all normalised maximum distances are obtained and then their median is taken and futher divided by log(number of facet levels). Different facet levels viz, 10, 20, 30, 40 are considered for a fixed x-axis level and data is simulated 200 times for each of these cases to learn about the distribution of these normalised distances through a histogram.

@@

>>>>

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
read_chunk('null_distribution.R')
```

@@

Null distribution of normalised maximum distances at this stage should be standardized Gumbel distribution. This is because we have assumed that distribution of JS distances are Normal and the maximum of such distances would follow a Gumbel distribution. When we normalise these maximum distances, ideally the distribution of those normalised distances should be standard Gumbel distribution (which is positively skewed).

@@

From the above graphs, we could see that irrespective of the levels, the distribution of the normalised distances look like a postively skewed distribution when the underlying observations are drawn from a N(5, 10) distribution. Let us check if the same holds true if the underlying distributions are from Exp(0.5), Chi-squared(5), Gumbel(0.5, 2). Here, we fix the number of levels to 20.

@@

For facets, first all normalised maximum distances are obtained and then their median is taken and futher divided by log(number of facet levels). Different facet levels viz, 10, 20, 30, 40 are considered for a fixed x-axis level and data is simulated 200 times for each of these cases to learn about the distributions.

### All levels drawn from Exp(2/3) distribution

@@

```{r normalallvar2}

It looks like the normalisation is also working at this stage.
